### 2022-05-18 supplement.Rmd
Save all tables as TSV

# Save the table
dir.create(tables_dir, showWarnings = FALSE)
write_csv(tabs1, file = here(tables_dir, "tabs1_experiments.csv"), na = "n/a")

@@

# Save the table
write_csv(tabs2, file = here(tables_dir, "tabs2_frequentist.csv"))

@@

  # Save the table
  write_csv(tabs3, file = here(tables_dir, "tabs3_jackknife.csv"))
}
```

@@

```{r, tabs3, include=TRUE}
# Read jackknife table from file
tabs3 <- read_csv(
  here(tables_dir, "tabs3_jackknife.csv"),
  col_types = "c", na = character()
)

@@

  # Create table for the meta-analysis of mental rotation performance
  sens %>%
    select(res, manipulation_name, manipulation_value) %>%
    pmap_dfr(function(res, manipulation_name, manipulation_value) {
      print_res_table(
        res,
        label_1 = manipulation_name, label_2 = manipulation_value,
        label_col_1 = "Manipulation", label_col_2 = " "
      )
    }) -> tabs7
  write_csv(tabs7, file = here(tables_dir, "tabs7_sens_meta.csv"))

  # Create table for the meta-regression of mental rotation performance
  sens %>%
    select(
      res_reg, manipulation_name, manipulation_value
    ) %>%
    pmap_dfr(function(res_reg, manipulation_name, manipulation_value) {
      print_res_reg_table(
        res_reg,
        label_1 = manipulation_name, label_2 = manipulation_value,
        label_col_1 = "Manipulation", label_col_2 = " "
      )
    }) -> tabs8
  write_csv(tabs8, file = here(tables_dir, "tabs8_sens_reg.csv"))

  # Create table for the meta-analysis of gender differences
  sens %>%
    filter(!map_lgl(res_gender, is.null)) %>%
    select(res_gender, manipulation_name, manipulation_value) %>%
    pmap_dfr(function(res_gender, manipulation_name, manipulation_value) {
      print_res_table(
        res_gender,
        label_1 = manipulation_name, label_2 = manipulation_value,
        label_col_1 = "Manipulation", label_col_2 = " "
      )
    }) -> tabs9
  write_csv(tabs9, file = here(tables_dir, "tabs9_sens_gender.csv"))
}
```

@@

```{r, tabs7, include=TRUE}
# Load sensitivity analysis table from file
tabs7 <- read_csv(
  here(tables_dir, "tabs7_sens_meta.csv"),
  col_types = "c", na = character(), trim_ws = FALSE
)

@@

```{r, tabs8, include=TRUE}
# Load sensitivity analysis table from file
tabs8 <- read_csv(
  here(tables_dir, "tabs8_sens_reg.csv"),
  col_types = "c", na = character(), trim_ws = FALSE
)

@@

```{r, tabs9, include=TRUE}
# Load sensitivity analysis table from file
tabs9 <- read_csv(
  here(tables_dir, "tabs9_sens_gender.csv"),
  col_types = "c", na = character(), trim_ws = FALSE
)

@@

# Save the tables
tabs10 <- tabs_correction$meta
tabs11 <- tabs_correction$gender
write_csv(tabs10, file = here(tables_dir, "tabs10_correction_meta.csv"))
write_csv(tabs11, file = here(tables_dir, "tabs11_correction_gender.csv"))
```

>>>>

# Save the table
dir.create(tables_dir, showWarnings = FALSE)
write_tsv(tabs1, file = here(tables_dir, "tabs1_experiments.tsv"), na = "n/a")

@@

# Save the table
write_tsv(tabs2, file = here(tables_dir, "tabs2_frequentist.tsv"))

@@

  # Save the table
  write_tsv(tabs3, file = here(tables_dir, "tabs3_jackknife.tsv"))
}
```

@@

```{r, tabs3, include=TRUE}
# Read jackknife table from file
tabs3 <- read_tsv(
  here(tables_dir, "tabs3_jackknife.tsv"),
  col_types = "c", na = character()
)

@@

  # Create table for the meta-analysis of mental rotation performance
  sens %>%
    select(res, manipulation_name, manipulation_value) %>%
    pmap_dfr(function(res, manipulation_name, manipulation_value) {
      print_res_table(
        res,
        label_1 = manipulation_name, label_2 = manipulation_value,
        label_col_1 = "Manipulation", label_col_2 = " "
      )
    }) -> tabs7
  write_tsv(tabs7, file = here(tables_dir, "tabs7_sens_meta.tsv"))

  # Create table for the meta-regression of mental rotation performance
  sens %>%
    select(
      res_reg, manipulation_name, manipulation_value
    ) %>%
    pmap_dfr(function(res_reg, manipulation_name, manipulation_value) {
      print_res_reg_table(
        res_reg,
        label_1 = manipulation_name, label_2 = manipulation_value,
        label_col_1 = "Manipulation", label_col_2 = " "
      )
    }) -> tabs8
  write_tsv(tabs8, file = here(tables_dir, "tabs8_sens_reg.tsv"))

  # Create table for the meta-analysis of gender differences
  sens %>%
    filter(!map_lgl(res_gender, is.null)) %>%
    select(res_gender, manipulation_name, manipulation_value) %>%
    pmap_dfr(function(res_gender, manipulation_name, manipulation_value) {
      print_res_table(
        res_gender,
        label_1 = manipulation_name, label_2 = manipulation_value,
        label_col_1 = "Manipulation", label_col_2 = " "
      )
    }) -> tabs9
  write_tsv(tabs9, file = here(tables_dir, "tabs9_sens_gender.tsv"))
}
```

@@

```{r, tabs7, include=TRUE}
# Load sensitivity analysis table from file
tabs7 <- read_tsv(
  here(tables_dir, "tabs7_sens_meta.tsv"),
  col_types = "c", na = character(), trim_ws = FALSE
)

@@

```{r, tabs8, include=TRUE}
# Load sensitivity analysis table from file
tabs8 <- read_tsv(
  here(tables_dir, "tabs8_sens_reg.tsv"),
  col_types = "c", na = character(), trim_ws = FALSE
)

@@

```{r, tabs9, include=TRUE}
# Load sensitivity analysis table from file
tabs9 <- read_tsv(
  here(tables_dir, "tabs9_sens_gender.tsv"),
  col_types = "c", na = character(), trim_ws = FALSE
)

@@

# Save the tables
tabs10 <- tabs_correction$meta
tabs11 <- tabs_correction$gender
write_tsv(tabs10, file = here(tables_dir, "tabs10_correction_meta.tsv"))
write_tsv(tabs11, file = here(tables_dir, "tabs11_correction_gender.tsv"))
```
